---
title: "EIH prediction using AI approaches"
author: "Félix Boudry"
date: "`r Sys.Date()`"
documentclass: article
classoption: oneside
lang: en-US
output:
  html_document:
    toc: yes
    number_section: yes
    fig_caption: yes
    keep_md: yes
  word_document:
    toc: yes
    number_sections: 4
    fig_caption: yes
  pdf_document:
    toc: yes
    toc_depth: 4
    number_sections: yes
    fig_caption: yes
    df_print: kable
    keep_md: yes
params:
  data:
    label: "Input dataset:"
    value: none
    input: file
  data_list:
    label: "List of files to import:"
    value: none
    input: text
  data_folder:
    label: "Path to multiple data sets folder:"
    value: ./Data
    input: text
bibliography: EIH_modeling.bib
---

```{r Setup, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  error = TRUE,
  message = FALSE,
  warning = FALSE
)

# Import libraries
source("./Scripts/Functions.R")
library(data.table)
library(tidyverse)
library(factoextra)
library(dbscan)
library(clusplus)
library(caret)
library(gbm)
library(lightgbm)
library(reticulate)
library(shapviz)
library(DiagrammeR)
library(magrittr)
library(gridExtra)
library(psych)
library(missRanger)
library(fs)
library(tcltk)
library(fossil)

# Run configuration
analysis_date <- format(Sys.time(), "%Y-%m-%d_%H.%M")
dir_create(path = paste0("Output/", analysis_date))

# Parameters for the analysis
new_LGBM_params <- TRUE
scale_data <- TRUE
cluster_number <- c(2, 4)
cluster_number_names <- list("two", "four")
dbscan_eps <- 10
dbscan_minPts <- 3
optics_eps <- 250
optics_minPts <- 5
optics_xi <- 0.1
lgbm_rounds <- 500
lgbm_split <- 0.65
optuna_rounds <- 200
optuna_trials <- 200
discriminating_variables <- c("saturation_rest",
                              "saturation_end",
                              "saturation_delta")
```

```{r Scripts, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
# Data to use
import_na_strings <- c("", " ", "na", "NA")
if (params$data != "none") {
  imported_data_names <- basename(params$data) %>% tools::file_path_sans_ext()
  imported_data <-
    params$data %>%
    read.csv(na.strings = import_na_strings) %>%
    lst()
} else if (params$data_list != "none") {
  imported_data_names <- basename(params$data_list) %>% tools::file_path_sans_ext()
  imported_data <-
    lapply(X = eval(parse(text = params$data_list)),
           FUN = read.csv,
           na.strings = import_na_strings)
} else {
  imported_data_names <- basename(params$data_folder) %>% tools::file_path_sans_ext()
  imported_data <-
    list.files(path = parse(text = params$data_folder) %>%
                 eval(),
               full.names = TRUE) %>%
    lapply(read.csv, na.strings = import_na_strings)
}

# Import files without knit for test purpose

# fileloc <- c("Data/absolute.csv", "Data/relative.csv")
# imported_data_names <- basename(fileloc) %>% tools::file_path_sans_ext()
# imported_data <- lapply(fileloc, read.csv) %>% `names<-`(imported_data_names)

# Sourcing scripts
compute_counter <- 1
for (analysis_data in imported_data) {
  tmp_env <- new.env()
  data_set_name <- imported_data_names[compute_counter]
  source("./Scripts/Unsupervised.R", local = tmp_env)
  # source("./Scripts/Supervised.R", local = tmp_env)
  
  old_names <- ls(envir = tmp_env)
  for (old_name in old_names) {
    new_name <- paste(old_name, data_set_name, sep = "_")
    assign(x = new_name, value = get(old_name, envir = tmp_env))
  }
  compute_counter <- compute_counter + 1
}
```

# Introduction

It is well known that endurance performances are limited by physiological
factors among which the cardio-respiratory is one of the most important
(@amannConvectiveOxygenTransport2008, @bassettLimitingFactorsMaximum2000). This
system can be limiting through different ways including the limitations of the
cardiac output (Qc), the oxygen diffusion or the pulmonary perfusion. Those
limitations can be enhanced by physical training and physiological adaptations
to exercise. Thus with training we can observe an increased cardiac output,
pulmonary perfusion or oxygen diffusion through an increased hemoglobin
concentration.

It's also well known that the environment can impact the oxygen pressures and
thus the inspired volume. This limitation is also present during
experimentation, like simulated altitude, during which the inspired fraction of
oxygen is diminished.

If the cardiac system is one of the most known limiting, the pulmonary system
can also participated in the observed limitations. This system is complicated
and the pulmonary anatomy is composed by several "section". A known
physiopathology impact athlete's performances is the exercise-induces hypoxemia
(EIH) (@raberinHypoxemieInduiteExercice2019). The purpose of this work is to be
able to classify athletes as EIH or NEIH without using the direct indicator
(saturation).

# Methods

## Subjects

```{r Subjects}
describe(x = analysis_data[c("age",
                             "height",
                             "weight")] , na.rm = T) %>%
  select(c("mean", "sd", "median", "min", "max")) %>%
  my_table(caption = "<center><strong>Données anthropologiques (n = 127)</center></strong>")
describe(x = analysis_data[c("train_years",
                             "train_volume")], na.rm = T) %>%
  select(c("mean", "sd", "median", "min", "max")) %>%
  my_table(caption = "<center><strong>Données d'entraînement des athlètes (n = 127)</center></strong>")
```

# Results

## Unsupervised learning

```{r Clustering results}
my_plot <- function(my_pat) {
  ls(pattern = paste0(my_pat, "_graph"), envir = .GlobalEnv) %>%
    lapply(get) %>%
    lapply(marrangeGrob,
           nrow = 1,
           ncol = 2,
           top = NULL) %>% 
    walk(print)
  ls(pattern = paste0(my_pat, "_confusion"), envir = .GlobalEnv) %>%
    lapply(get)
}

my_plot2 <- function(my_pat) {
  ls(pattern = paste0(my_pat, "_graph"), envir = .GlobalEnv) %>%
    lapply(get) %>% 
    walk(print)
  ls(pattern = paste0(my_pat, "_rand"), envir = .GlobalEnv) %>%
    lapply(get)
}

ls(pattern = "^kclust_coord", envir = .GlobalEnv) %>%
    lapply(get) %>% 
    lapply(marrangeGrob,
           nrow = 1,
           ncol = 2,
           top = NULL) %>%
    walk(print)
my_plot("^kclust")
my_plot("^hclust")
my_plot2("^dbscan")
my_plot2("^optics")
```

## Supervised learning

```{r LGBM results}
lgbm_confusion$overall

t(as.data.frame(lgbm_model$params[c(
  "boosting",
  "lambda_l1",
  "lambda_l2",
  "num_leaves",
  "max_depth",
  "feature_fraction",
  "bagging_fraction",
  "bagging_freq",
  "learning_rate"
)])) %>% my_table()
lgbm_confusion
lgbm_importance_plot %>%
  lgb.plot.importance()
lgbm_importance_plot %>%
  lgb.plot.interpretation()
lgbm_plot %>%
  walk(print)
```

# References

<div id="refs"></div>

```{r End_tasks, include=FALSE}
# dir_copy(path = "./figure/",
#          new_path = paste0("Output/", analysis_date))
# dir_delete(path = "./figure/")
save.image(file = paste0("./Output/", analysis_date, "/global.RData"))
```

