---
title: "EIH Model"
author: "Félix Boudry"
date: "`r Sys.Date()`"
documentclass: article
classoption: oneside
lang: en-US
output:
  html_document: 
    toc: yes
    number_section: yes
    fig_caption: yes
  word_document:
    toc: yes
    number_sections: 4
    fig_caption: yes
  pdf_document: 
    toc: yes
    toc_depth: 4
    number_sections: yes
    fig_caption: yes
    df_print: kable
bibliography: EIH_modeling.bib
---

```{r Setup, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	error = TRUE,
	message = FALSE,
	warning = FALSE
)

# Import libraries
library(tidyverse)
library(readxl)
library(data.table)
library(janitor)
library(fs)
library(FactoMineR)
library(missMDA)
library(CatEncoders)
library(factoextra)
library(clusplus)
library(dbscan)
library(caret)
library(gbm)
library(lightgbm)
library(reticulate)
library(shapviz)
library(DiagrammeR)
library(kableExtra)
library(grDevices)
library(psych)
library(gridExtra)
library(ggplotify)
```

```{r Scripts, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
# Sourcing scripts
# Some parameters need configuration :
# - Cluster number has to be specified in the "Descriptive.R" script
# - eps and MinPts have to be specified for DBScan clustering
source("./Scripts/Functions.R")
source("./Scripts/Import.R")
source("./Scripts/Compute.R")
source("./Scripts/Descriptive.R")
source("./Scripts/Predictive.R")
```

```{r}
load(file = "./Environments/predictive.RData")
```

# Introduction

It is well known that endurance performances are limited by physiological
factors among which the cardio-respiratory is one of the most important
(@amannConvectiveOxygenTransport2008, @bassettLimitingFactorsMaximum2000). This
system can be limiting through different ways including the limitations of the
cardiac output (Qc), the oxygen diffusion or the pulmonary perfusion. Those
limitations can be enhanced by physical training and physiological adaptations
to exercise. Thus with training we can observe an increased cardiac output,
pulmonary perfusion or oxygen diffusion through an increased hemoglobin
concentration.

It's also well known that the environment can impact the oxygen pressures and
thus the inspired volume. This limitation is also present during
experimentation, like simulated altitude, during which the inspired fraction of
oxygen is diminished.

If the cardiac system is one of the most known limiting, the pulmonary system
can also participated in the observed limitations. This system is complicated
and the pulmonary anatomy is composed by several "section". A known
physiopathology impact athlete's performances is the exercise-induces hypoxemia
(EIH) (@raberinHypoxemieInduiteExercice2019). The purpose of this work is to be
able to classify athletes as EIH or NEIH without using the direct indicator
(saturation).

# Methods

## Subjects

```{r}
describe(my_data$infos, na.rm = T) %>%
  select(c("mean", "sd", "median", "min", "max")) %>%
  subset(rownames(.) %in% c("age", "height", "weight", "saturation_end")) %>%
  my_table(caption = "<center><strong>Données anthropologiques (n = 127)</center></strong>")
describe(my_data$infos, na.rm = T) %>%
  select(c("mean", "sd", "median", "min", "max")) %>%
  subset(rownames(.) %in% c("train_volume", "train_years")) %>%
  my_table(caption = "<center><strong>Données d'entraînement des athlètes (n = 127)</center></strong>")
table(my_data$inf$sport) %>%
  my_table(col.names = c("Sport", "Freq"),
           caption = "<center><strong>Sports pratiqués (n = 127)</center></strong>")
```

# Results

## Descriptive

### Absolute

```{r}
my_results$cluster_results_absolute$cluster_number_graph %>%
  marrangeGrob(ncol = 2, nrow = 2, top = NULL)
my_results$cluster_results_absolute$kclust$graph %>%
  marrangeGrob(ncol = 2, nrow = 1, top = NULL)
my_results$cluster_results_absolute$kclust$coord %>%
  marrangeGrob(ncol = 1, nrow = 2, top = NULL)
my_results$cluster_results_absolute$hclust$graph$two
my_results$cluster_results_absolute$hclust$graph$four
my_results$cluster_results_absolute$dbscan$graph
my_results$cluster_results_absolute$optics$graph
my_results$cluster_results_absolute$boxplots %>%
  lapply(
    X = .,
    FUN = marrangeGrob,
    ncol = 2,
    nrow = 2,
    top = NULL
  ) %>%
  walk(print)
my_results$cluster_results_absolute$eih_repartition %>%
  lapply("[[", "eih") %>%
  lapply(as.grob) %>%
  marrangeGrob(ncol = 2, nrow = 2, top = NULL)
my_results$cluster_results_absolute$eih_severity_repartition %>%
  lapply("[[", "eih_severity") %>%
  lapply(as.grob) %>%
  marrangeGrob(ncol = 2, nrow = 2, top = NULL)
```

### Relative

```{r}
my_results$cluster_results_relative$cluster_number_graph %>%
  marrangeGrob(ncol = 2, nrow = 2, top = NULL)
my_results$cluster_results_relative$kclust$graph %>%
  marrangeGrob(ncol = 2, nrow = 1, top = NULL)
my_results$cluster_results_relative$kclust$coord %>%
  marrangeGrob(ncol = 1, nrow = 2, top = NULL)
my_results$cluster_results_relative$hclust$graph$two
my_results$cluster_results_relative$hclust$graph$four
my_results$cluster_results_relative$dbscan$graph
my_results$cluster_results_relative$optics$graph
my_results$cluster_results_relative$boxplots %>%
  lapply(
    X = .,
    FUN = marrangeGrob,
    ncol = 2,
    nrow = 2,
    top = NULL
  ) %>%
  walk(print)
my_results$cluster_results_relative$eih_repartition %>%
  lapply("[[", "eih") %>%
  lapply(as.grob) %>%
  marrangeGrob(ncol = 2, nrow = 2, top = NULL)
my_results$cluster_results_relative$eih_severity_repartition %>%
  lapply("[[", "eih_severity") %>%
  lapply(as.grob) %>%
  marrangeGrob(ncol = 2, nrow = 2, top = NULL)
```

### PCA based

```{r}
my_results$cluster_results_PCA$cluster_number_graph %>%
  marrangeGrob(ncol = 2, nrow = 2, top = NULL)
my_results$cluster_results_PCA$kclust$graph %>%
  marrangeGrob(ncol = 2, nrow = 1, top = NULL)
my_results$cluster_results_PCA$kclust$coord %>%
  marrangeGrob(ncol = 1, nrow = 2, top = NULL)
my_results$cluster_results_PCA$hclust$graph$two
my_results$cluster_results_PCA$hclust$graph$four
my_results$cluster_results_PCA$dbscan$graph
my_results$cluster_results_PCA$optics$graph
my_results$cluster_results_PCA$boxplots %>%
  lapply(
    X = .,
    FUN = marrangeGrob,
    ncol = 2,
    nrow = 2,
    top = NULL
  ) %>%
  walk(print)
my_results$cluster_results_PCA$eih_repartition %>%
  lapply("[[", "eih") %>%
  lapply(as.grob) %>%
  marrangeGrob(ncol = 2, nrow = 2, top = NULL)
my_results$cluster_results_PCA$eih_severity_repartition %>%
  lapply("[[", "eih_severity") %>%
  lapply(as.grob) %>%
  marrangeGrob(ncol = 2, nrow = 2, top = NULL)
```

## Predicitve

```{r}
my_results$my_models_absolute$gbm_caret_model_results$gbm_result$stat$overall
my_results$my_models_absolute$gbm_model_results$gbm_result$stat$overall
my_results$my_models_absolute$lgbm_model_results$lgbm_confusion$overall
my_results$my_models_relative$gbm_caret_model_results$gbm_result$stat$overall
my_results$my_models_relative$gbm_model_results$gbm_result$stat$overall
my_results$my_models_relative$lgbm_model_results$lgbm_confusion$overall
my_results$my_models_PCA$lgbm_model_results$lgbm_confusion$overall
```

### Absolute

```{r}
my_results$my_models_absolute$gbm_model_results$gbm_result[c("stat", "importance_plot")]
my_results$my_models_absolute$gbm_caret_model_results$gbm_result[c("stat", "importance_plot")]
t(
  as.data.frame(
    my_results$my_models_absolute$lgbm_model_results$lgbm_model$params[c(
      "boosting",
      "lambda_l1",
      "lambda_l2",
      "num_leaves",
      "max_depth",
      "feature_fraction",
      "bagging_fraction",
      "bagging_freq",
      "learning_rate"
    )]
  )
) %>% my_table()
my_results$my_models_absolute$lgbm_model_results$lgbm_confusion
my_results$my_models_absolute$lgbm_model_results$lgbm_importance_plot %>% 
  lgb.plot.importance()
my_results$my_models_absolute$lgbm_model_results$lgbm_importance_plot %>% 
  lgb.plot.interpretation()
my_results$my_models_absolute$lgbm_model_results$lgbm_plot %>% 
  walk(print)
```

### Relative

```{r}
my_results$my_models_relative$gbm_model_results$gbm_result[c("stat", "importance_plot")]
my_results$my_models_relative$gbm_caret_model_results$gbm_result[c("stat", "importance_plot")]
t(
  as.data.frame(
    my_results$my_models_relative$lgbm_model_results$lgbm_model$params[c(
      "boosting",
      "lambda_l1",
      "lambda_l2",
      "num_leaves",
      "max_depth",
      "feature_fraction",
      "bagging_fraction",
      "bagging_freq",
      "learning_rate"
    )]
  )
) %>% my_table()
my_results$my_models_relative$lgbm_model_results$lgbm_confusion
my_results$my_models_relative$lgbm_model_results$lgbm_importance_plot %>% 
  lgb.plot.importance()
my_results$my_models_relative$lgbm_model_results$lgbm_importance_plot %>% 
  lgb.plot.interpretation()
my_results$my_models_relative$lgbm_model_results$lgbm_plot %>% 
  walk(print)
```

### PCA

```{r}
my_results$my_models_PCA$gbm_model_results$gbm_result[c("stat", "importance_plot")]
my_results$my_models_PCA$gbm_caret_model_results$gbm_result[c("stat", "importance_plot")]
t(
  as.data.frame(
    my_results$my_models_PCA$lgbm_model_results$lgbm_model$params[c(
      "boosting",
      "lambda_l1",
      "lambda_l2",
      "num_leaves",
      "max_depth",
      "feature_fraction",
      "bagging_fraction",
      "bagging_freq",
      "learning_rate"
    )]
  )
) %>% my_table()
my_results$my_models_PCA$lgbm_model_results$lgbm_confusion
my_results$my_models_PCA$lgbm_model_results$lgbm_importance_plot %>% 
  lgb.plot.importance()
my_results$my_models_PCA$lgbm_model_results$lgbm_importance_plot %>% 
  lgb.plot.interpretation()
my_results$my_models_PCA$lgbm_model_results$lgbm_plot %>% 
  walk(print)
```

# References

<div id="refs"></div>
