---
title: "Result_template"
author: "Félix Boudry"
date: "`r Sys.Date()`"
output: html_document
---

```{r message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

# `r paste(my_env$name)`

## Material and methods

### Subjects

The data from the data set _**`r paste(my_env$name)`**_ are characterized by the
following features:

```{r}
describe(x = antrop_data, na.rm = T) %>%
  round() %>%
  select(c("mean", "sd", "median", "min", "max")) %>%
  my_table(
    caption = paste0(
      "<center><strong>Anthropological values (n = ",
      nrow(analysis_data) ,
      ")</center></strong>"
    )
  )
```

## Results

### Unsupervised learning

The unsupervised approach is based on algorithms that don't need labels to
create a classification. This mainly include clustering algorithms such as
k-means and hierarchical clustering.

#### K-means clustering

```{r fig.align='center'}
kclust_graph
kclust_coord
kclust_confusion$table %>%
  my_table(caption = "<center><strong>K-means confusion matrix</center></strong>", row.names = TRUE) %>%
  kableExtra::column_spec(1, bold = TRUE)
kclust_confusion$overall %>%
  my_table(caption = "<center><strong>Overall metrics</center></strong>", col.names = NULL)
kclust_confusion$byClass %>%
  my_table(caption = "<center><strong>Metrics by class</center></strong>", col.names = NULL)
```

#### Hierarchical agglomerative clustering

```{r fig.align='center'}
hclust_bu_graph
hclust_bu_confusion$table %>%
  my_table(caption = "<center><strong>HC agglomerative confusion matrix</center></strong>", row.names = TRUE) %>%
  kableExtra::column_spec(1, bold = TRUE)
hclust_bu_confusion$overall %>% my_table(caption = "<center><strong>Overall metrics</center></strong>", col.names = NULL)
hclust_bu_confusion$byClass %>%
  my_table(caption = "<center><strong>Metrics by class</center></strong>", col.names = NULL)
```

#### Hierarchical divisive clustering

```{r fig.align='center'}
hclust_td_graph
hclust_td_confusion$table %>%
  my_table(caption = "<center><strong>HC divisive confusion matrix</center></strong>", row.names = TRUE) %>%
  kableExtra::column_spec(1, bold = TRUE)
hclust_td_confusion$overall %>% my_table(caption = "<center><strong>Overall metrics</center></strong>", col.names = NULL)
hclust_td_confusion$byClass %>%
  my_table(caption = "<center><strong>Metrics by class</center></strong>", col.names = NULL)
```

### Supervised learning

The supervised approach, compared to the unsupervised one, require labels to try
a classification and the correct the classification process and criteria. In
this work we used LGBM and XGboost and decision tree based methods and a Dense
and a NODE model as neural network approaches.

#### LightGBM

The best LGBM model computed by Optuna has a accuracy of 
**`r optuna_lgbm_best_accuracy`**. The model computed with the best 
parameters of this trial has the following metrics:

```{r fig.align='center'}
# Confusion tables
lgbm_confusion$table %>%
  my_table(caption = "<center><strong>LGBM confusion matrix</center></strong>", row.names = TRUE) %>%
  kableExtra::column_spec(1, bold = TRUE)
lgbm_confusion$overall %>% my_table(caption = "<center><strong>Overall metrics</center></strong>", col.names = NULL)
lgbm_confusion$byClass %>%
  my_table(caption = "<center><strong>Metrics by class</center></strong>", col.names = NULL)

# LGBM parameters
lgbm_best_params %>%
  as.data.frame() %>%
  t() %>%
  my_table(caption = "<center><strong>Best Optuna parameters</center></strong>")

# SHAP plots
lgbm_shap_plot %>%
  walk(print)
```

#### XGBoost

The best XGboost model computed by Optuna has a accuracy of 
**`r optuna_xgb_best_accuracy`**. The model computed with the best parameters of
this trial has the following metrics:

```{r fig.align='center'}
# Confusion tables
xgboost_confusion$table %>%
  my_table(caption = "<center><strong>XGBoost confusion matrix</center></strong>", row.names = TRUE) %>%
  kableExtra::column_spec(1, bold = TRUE)
xgboost_confusion$overall %>% my_table(caption = "<center><strong>Overall metrics</center></strong>", col.names = NULL)
xgboost_confusion$byClass %>%
  my_table(caption = "<center><strong>Metrics by class</center></strong>", col.names = NULL)

# XGBoost parameters
xgboost_best_params %>%
  as.data.frame() %>%
  t() %>%
  my_table(caption = "<center><strong>Best Optuna parameters</center></strong>")

# SHAP plots
xgboost_shap_plot %>%
  walk(print)
```

#### Keras

```{r fig.align='center'}

```

#### PyTorch Tabular NODE

```{r fig.align='center'}
node_accuracy
node_kappa
node_f1
node_confusion
node_auc_roc
node_precision
node_recall
```

## Models comparison

```{r fig.align='center'}
result_list <-
  lst(
    results_lgbm = lst(
      lgbm_accuracy,
      lgbm_kappa,
      lgbm_f1,
      lgbm_auc_roc,
      lgbm_precision,
      lgbm_recall
    ),
    results_xgboost = lst(
      xgboost_accuracy,
      xgboost_kappa,
      xgboost_f1,
      xgboost_auc_roc,
      xgboost_precision,
      xgboost_recall
    ),
    results_node = lst(
      node_accuracy,
      node_kappa,
      node_f1,
      node_auc_roc,
      node_precision,
      node_recall
    )
  )

do.call(rbind, result_list) %>%
  `colnames<-`(c("Accuracy",
                 "Kappa",
                 "F1",
                 "AUC-ROC",
                 "Precision",
                 "Recall")) %>%
  `rownames<-`(c("LGBM", "XGBoost", "NODE")) %>%
  my_table()
```

